---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lemonmarkets

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/lemonmarkets)](https://CRAN.R-project.org/package=lemonmarkets)
[![R-CMD-check](https://github.com/quantargo/lemonmarkets/workflows/R-CMD-check/badge.svg)](https://github.com/quantargo/lemonmarkets/actions)
<!-- badges: end -->

The goal of lemonmarkets is to provide an R interface to the [lemon.markets](https://lemon.markets) trading API. The API docs are available at [docs.lemon.markets](https://docs.lemon.markets).

## Installation

You can install the development version of lemonmarkets like so:

``` r
remotes::install_github("quantargo/lemonmarkets")
```

## Get Started

Before you can get started with the lemonmarkets API you need to get an API key from the [web page ](https://www.lemon.markets). Currently there is still a waitlist since the service is not publicly available yet. 

After you acquired the API keys we recommend to create a new file `.Renviron` within your R project directory and enter the keys there:

```{bash, eval=FALSE}
LEMON_MARKETS_CLIENT_ID=<your-client-id>
LEMON_MARKETS_CLIENT_SECRET=<your-client-secret>
```

The `LEMON_MARKETS_CLIENT_ID` and `LEMON_MARKETS_CLIENT_SECRET` are then available as environment variables within your R session. Alternatively, you can also set the environment variables directly within the R session as

```{r, eval=FALSE}
Sys.setenv(LEMON_MARKETS_CLIENT_ID="<your-client-id>",
           LEMON_MARKETS_CLIENT_SECRET="<your-client-secret>")
```

Once you have set the environment variables you can load the lemonmarkets package and get your access token through the `auth()` function:

```{r example}
library(lemonmarkets)

auth()
```

All subsequent calls will use the resulting access token which is stored in `options("LEMON_MARKETS_TOKEN")`.

Currenly, all trading operations are done through pre-defined sub-accounts (spaces).
These spaces need to be created via the web fronted to retrieve its ID.

## Searching for an instrument

You can search for an instrument, like Daimler stock, through `instrument_search()`:

```{r}
instruments_search(list(search = "daimler", type = "stock"))
```

## Retrieving Market Data

To retrieve historical Open-High-Low-Close (OHCL) data for the German Daimler listing you can use the `ohcl()` function:

```{r}
ohcl("DE0007100000", from = Sys.Date() - 7, freq = "daily")
```
The example above retrieves daily data for the last week. Also other frequencies
like like `hourly` and `min` (minute) are available. 

Alternatively, you can also use `quotes()` to only retrieve the last market quote
for an instrument:

```{r}
quotes("DE0007100000")
```

## Get Current Cash Balance

The current cash balance of a specified space can be retrieved as

```{r}
space_id <- "e44907b7-d131-4ec9-9647-a2649480003d"
bal <- balance(space_id)
```

## Place an Order

You can place an order with the `create_order()` function. To place a market order of 5 shares for Daimler stock we can use

```{r, eval=FALSE, echo=TRUE}
create_order(space_id, "DE0007100000", 5)
```

Note, that orders are immediatly activated per default. You can disable this 
features through the parameter `activate=FALSE`.


## Get Current Portfolio

To get a list of the current portfolio we can use

```{r}
portfolio(space_id)
```


## Quantargo Workspace Trading Example

The link below contains a fully-functioning Quantargo workspace which
uses the package to daily rebalance a mean-reversion portfolio strategy:


## Feedback

Please raise an issue through Github.

